BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for BPMN Models

### 2024-07-03 main.tex
Cleanup
Introduction

%% hf: enable header and footer.
\documentclass[
twocolumn,
% hf,
]{ceurart}

@@

\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for Realistic BPMN Models}

@@

\maketitle

% Details can be found here: https://bpm2024.agh.edu.pl/call-for-demos-and-resources/
% 5 pages including references
% Extended version on GitHub and then on Arxiv once submitted

% An introduction section, which, among others, should highlight the significance of the tool or resource to the BPM field;
\section{Introduction}
The tool is available online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}.
% Why is it significant for the BPM field?

\begin{figure}[ht]
	\centering
	\includegraphics[width=\linewidth]{images/overview}
	\caption{Overview of the tool}
	\label{fig:overview}
\end{figure}

% Must have section according to the description
% A section discussing the innovations of the tool or resource to the BPM community and its main characteristics or features
\section{Innovations} % Main tool description and showing the innovations
Three main innovations of the tool:
% Instantaneous
% Comprehensible
% Fixable

\section{Maturity of the tool}
% Scalability tests (instantaneous)
Improves upon our previous BPMN Analyzer tool~\cite{krauterFormalizationAnalysisBPMN2023}.
% bpmn.io forum link/mention: https://forum.bpmn.io/t/automatic-bpmn-control-flow-analysis-and-resolution/11150

@@

\section{Related work?}
% Could cite my other extended version and put that on arxiv.

\section{Conclusion \& future work}

@@

% If your work has an appendix, this is the place to put it.
% \appendix

>>>>

%% hf: enable header and footer.
\documentclass[
% hf, % <-- Not sure if this should be enabled
]{ceurart}

@@

\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for BPMN Models}

@@

\maketitle
% 5 pages including references

% Extended version on GitHub and then on Arxiv once submitted

% An introduction section, which, among others, should highlight the significance of the tool or resource to the BPM field;
\section{Introduction}

% Problem statement
Business Process Modeling Notation (BPMN) is becoming increasingly popular for automating processes and orchestrating people and systems.
However, many process models suffer from control-flow anomalies, such as deadlocks, livelocks, starvation, and lack of synchronization~\cite{fahlandAnalysisDemandInstantaneous2011}.
These errors hinder the correct execution of BPMN models and may be detected late in the development process, resulting in elevated costs.

% Solution
In this paper, we describe a new tool, the \textit{BPMN Analyzer 2.0}\footnote{
In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in \cite{krauterFormalizationAnalysisBPMN2023}.}, for analyzing BPMN process models to detect control-flow anomalies \textit{already} during modeling.
\autoref{fig:overview} shows an overview of the tool.
The tool front-end is based on the popular \textit{bpmn.io} ecosystem, while the analysis is implemented in Rust for performance and memory efficiency reasons.
The BPMN Analyzer is open-source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}~\cite{timkrauterBPM2024Artifacts2024}.

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.6\linewidth]{images/overview}
	\caption{Overview of the BPMN Analyzer 2.0}
	\label{fig:overview}
\end{figure}

The tool can check models after each change since analysis is \textit{instantaneous} according to \cite{fahlandAnalysisDemandInstantaneous2011}, i.e., it takes 500ms or less.
Furthermore, we ensure the results are \textit{comprehensible} by highlighting possible violations directly in the model and displaying an interactive counterexample visualization.
Finally, the tool suggests \textit{fixes} for the most common soundness violations and can be extended to suggest more fixes in the future.
However, the BPMN analyzer cannot provide fixes for all possible violations due to the wide variety of possible control-flow anomalies in BPMN models.

% Why is it significant for the BPM field?
Fahland et al.~\cite{fahlandAnalysisDemandInstantaneous2011} describe \textit{coverage}, \textit{immediacy}, and \textit{consumability} as the main challenges for users unaccustomed to formal analysis methods.
The BPMN Analyzer addresses all these challenges since it supports the most common BPMN elements used in practice (coverage), provides \textit{instantaneous} results (immediacy), and a \textit{comprehensible} user interface (consumability), even including suggestions of fixes.
Developers of industrial BPMN solutions also like our tool, especially the End-2-End user journey\footnote{\url{https://forum.bpmn.io/t/automatic-bpmn-control-flow-analysis-and-resolution/11150}}.
Thus validating our claim of a UI that is understandable for users unfamiliar with formal analysis methods.

% Paper structure
In the remainder of the paper, we describe how instantaneous, comprehensible, and fixable anomaly detection is achieved in \autoref{sec:innovations}.
Then, we discuss the maturity of our tool in \autoref{sec:maturity} before presenting related work in \autoref{sec:related-work}.
Finally, we conclude in \autoref{sec:conclusion}.

% Must have section according to the description
% A section discussing the innovations of the tool or resource to the BPM community and its main characteristics or features
\section{Innovations} \label{sec:innovations} % Main tool description and showing the innovations
Three main innovations of the tool:
% Instantaneous
% Comprehensible
% Fixable

% They also want this section
\section{Maturity of the tool} \label{sec:maturity}
% Discuss/highlight the implementation: Test cases, static analysis etc. industrial standard! ;)
% Scalability tests (instantaneous) --> Generated models are public including our tool for future direct comparisons
Improves upon our previous BPMN Analyzer tool~\cite{krauterFormalizationAnalysisBPMN2023}.

% bpmn.io forum link/mention: https://forum.bpmn.io/t/automatic-bpmn-control-flow-analysis-and-resolution/11150

% TODO: Update DOI link to fit the extended version on arxiv
% Extended version: \cite{krauterInstantaneousComprehensibleFixable2024}

Artifacts: \cite{timkrauterBPM2024Artifacts2024}

\section{Related work?} \label{sec:related-work}

% Breakdown of BPMN coverage: https://github.com/timKraeuter/rust_bpmn_analyzer?tab=readme-ov-file#bpmn-coverage

\section{Conclusion \& future work} \label{sec:conclusion}

@@

@@
